Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-05 neurips-20/cvx-flats.tex
broader impacts pass

\section*{Broader Impact}
A general framework to design consistent convex surrogate losses would have broad impact throughout the applications of machine learning in society.
Moreover, in problems such as structural prediction, knowing the lowest possible prediction dimension for a consistent surrogate is crucial for practical performance.
Our work advances understanding in both of these questions, and takes an important step toward a general framework which could lead to new surrogates for prediction tasks both new and old.

>>>>

\section*{Broader Impacts}
\paragraph{Background: surrogate losses and dimension.} There are numerous and growing applications, well-known to readers in the field, of supervised machine learning where we learn, from training data pairs $(x,y)$, to predict $y$ from $x$.
Essentially the only known approach to this problem is to train a model to minimize \emph{loss} on the training data; and essentially the only practically-used losses are convex losses on $\reals^d$, generally surrogates for a target loss (such as 0-1 loss for classification) or target statistic to be estimated (such as the conditional median or variance of $y$ given $x$).

This paper may not be relevant to all of these problems, but it is especially relevant where the surrogate prediction space is high-dimensional.
This can include \emph{structured prediction} problems where the goal is to learn to predict properties like rankings of labels by likelihood, or predicting parse trees from natural language sentences.
It can also include standard classification tasks where we would like to embed the thousand or more possible labels into a smaller-dimensional prediction space.
In all of these settings, a lower prediction dimension can translate to improved computation time and reduced sample complexity, allowing algorithms to provide more accurate predictions with less data and compute.

\paragraph{Impact via influence on downstream research.}
This paper takes just one small step, but still a step, toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
The theory in this paper may help practitioners in a number of ways.
Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to elicit, either directly or indirectly.
As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best base, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.

Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts appears very difficult to foresee.

%% Bo: rewritten Jun 4 8pm
% A general framework to design consistent convex surrogate losses would have broad impact throughout the applications of machine learning in society.
% Moreover, in problems such as structural prediction, knowing the lowest possible prediction dimension for a consistent surrogate is crucial for practical performance.
% Our work advances understanding in both of these questions, and takes an important step toward a general framework which could lead to new surrogates for prediction tasks both new and old.
